Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
responded to peters section 3 comments

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.  We circumvent this issue by working with the orders of zeros and poles relative to the divisor we are inducting from, rather than relative to the structure sheaf.\todo{Peter: This last sentence is kind of awkward.  I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner... I hope...}

@@

\begin{rem}
Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
\end{rem}
\todo{Peter: I'm not sure how useful this remark is.  After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.  The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}

@@

The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}. Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}.  \todo{Peter: In general, I'm not sure how important it is for us to draw all the analogs between your definition and proofs and those of VZB.  As long as we make not in the section's introduction that they are similar, we might leave it out of the remaining transitions and remarks.}

\begin{lem}
\label{lem:admissible_inequality}
Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
stronger condition \todo{Peter: How is it a stronger condition if it implied by that of (Ad-ii).  If $a\implies b$ then $b$ is by definition a weaker condition right?  I agree that the latter condition is somehow better, but it seems inaccurate to call it stronger.  I may be being over picky here...} that

@@

We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
analog of ~\cite[Theorem 8.5.7]{vzb:stacky}.

@@

\todo{Add conclusion to section}

>>>>

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections. We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.\todo{Peter: This last sentence is kind of awkward.  I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner... I hope... Aaron: I changed it. Is it better now?}

@@

\iffalse
\begin{rem}
Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
\end{rem}
\todo{Peter: I'm not sure how useful this remark is.  After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.  The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
\fi

@@

The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.

\begin{lem}
\label{lem:admissible_inequality}
The inequality (Ad-ii) of Definition ~\ref{defn:admissible} implies the
tighter inequality that

@@

@@

\todo{Add conclusion to section. Aaron: Should we have conclusions?}
